\documentclass[9pt,a4paper,sans]{moderncv}
\moderncvstyle{casual} % CV theme - options input: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}
\usepackage{lipsum}
\usepackage[scale=0.75]{geometry}

\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
%%\usepackage[spanish]{babel}
\usepackage{bibunits}
\usepackage{xcolor}

\newcommand{\ts}{\textsuperscript}
\newcommand{\Q}{{\textsf{Q}\hspace*{-1.1ex}%
  \rule{0.15ex}{1.5ex}\hspace*{1.1ex}}}
\newcommand{\Cuat}{\ts{o}\Q~}
\newcommand{\actual}{$\infty$}
\newcommand{\vat}{CUIT}
\newcommand{\birthdate}{Fecha de Nacimiento}


\firstname{Cristian Sebastian}
\familyname{Rocha}

\title{Curriculum Vitae}
\address{Lavalle 2294 2\ts{o}}{Villa Ballester, Buenos Aires (1653)}
\phone[mobile]{(+54-911)~6800~0269}
\email{csrocha@gmail.com}
\homepage{http://www.github.com/csrocha/}

\extrainfo{Birth Date 4 dic 1975}
%\photo[70pt][0pt]{csrocha.png} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"The important thing, once you have enough to eat and a nice house, is what you can do for others, what you can contribute to the enterprise as a whole." - Donald Knuth}

\newcommand{\DC}{Computer Department}
\newcommand{\FCEN}{Faculty of Science}
\newcommand{\UBA}{University of Buenos Aires}
\newcommand{\CS}{MSc in Computer Science}

\begin{document}

\makecvtitle

\section{Professional Background}\label{profesional:desde}

\cventry{2022-\actual}
	{Chief Technology Officer}
	{Fundación Observatorio PyME}
	{Buenos Aires, Argentina}
	{}
	{
        As the CTO at Fundación Observatorio PyME, I have been entrusted with key responsibilities, including:
	\begin{description}
        \item [Data Curation Infrastructure:] Overseeing the establishment and management of data curation infrastructure, ensuring accurate and reliable data processing to generate economic, structural, and sector-specific indicators for SMEs.
        \item [Product Development:] Leading the development of innovative products leveraging the generated indicators, such as creating user-friendly applications and online platforms to provide stakeholders with access to relevant and actionable data.
        \item [Technological Strategy:] Defining and spearheading the company's technological strategy, exploring and adopting cutting-edge technologies, implementing software systems, and identifying opportunities to enhance efficiency and productivity.
        \item [Development and Maintenance:] Supervising the development and maintenance of robust systems and tools, including software and hardware, to guarantee seamless operations and optimal performance.
        \item [Technology Team Leadership:] Providing visionary leadership to the technology team, fostering a high-performing and motivated workforce of programmers, software engineers, database administrators, and technology professionals. Setting clear objectives, monitoring performance, and offering guidance to achieve success.
        \item [Data Security and Privacy:] Ensuring the utmost security and privacy of sensitive company data by implementing information security policies, conducting risk assessments, and swiftly responding to potential security incidents.
        \item [Collaboration with Business Leaders:] Collaborating closely with other business leaders, such as the Foundation's General Director, Research Director, and Finance Director, to align technological strategies with overall business goals. Presenting reports on technology's impact and contributing to broader business initiatives.
        \item [Information Provider Interaction:] Engaging with external information providers to source relevant data for indicator generation, evaluating and acquiring information from diverse sources, and optimizing data acquisition and processing.
        \item [Project Management:] Efficiently managing technology-related projects, coordinating product development initiatives, resource allocation, and ensuring timely and successful project completion.
	\end{description}
This role has provided a rewarding opportunity to contribute to the foundation's growth and success, aligning technological advancements with the mission to support SMEs in Argentina.
	}
\cventry{2022-\actual}
	{Founder Partner}
	{Moldeo Interactive}
	{Paris, France}
	{}
	{
	As a Founder Partner at Moldeo Interactive, I played a pivotal role in the company's inception and growth.
	Over the years, the company evolved into a successful SA in France.
	Recently, I have been approached by the company to assist in brand development, leverage my expertise, and explore new initiatives within the organization.
	Currently, I am actively involved in adapting to the company's successful projects, such as the Odoo module for Mercado Libre.
	I am delving into the existing state of the project, contributing to the definition of its roadmap and solutions.
	Moreover, I am directly contributing by proposing innovative solutions in Extended Reality (XR) for Odoo.
	To foster collaboration and engagement, I have initiated a community on GitHub dedicated to these objectives.
	In addition to my technical contributions, I am also an active writer on the company's blog.
	Through my posts, I introduce, explain, and explore new ideas in the realm of infrastructure and emerging technologies associated with Moldeo Interactive's solutions.
	Being a Founder Partner at Moldeo Interactive has provided me with a unique opportunity to shape the company's trajectory and contribute to its ongoing success.
	I am excited to continue my journey with the company, driving innovation and creating a lasting impact in the technology landscape.
	}
\cventry{2012-\actual}
	{Geostatistical research team member}
	{Argentine PyMES Observatory - University of Bolognia}
	{Buenos Aires, Argentina}
	{Computer science consultant, engineering and developer}
	{\begin{description}
	 \item [Consultant] Design and implement statistical methods for geo-classification.
	 \item [Developer] Develop ETL, training task for statistical models on R.
	 \item [Engineering] Design and setup of solution infrastructure.
         \end{description}}
\cventry{2019-2022}
	{IA Infrastructure Engineering}
	{Mercado Libre}
	{Buenos Aires, Argentina}
	{}
	{\begin{description}
	 \item [Platform Machine Learning] Member of the core team of the main Mercado Libre Machine Learning solution. Analysis, engineering, and development of core system at different levels: SDK, CLI, Web Front End, Scheduler, Queues, Pipelines on AWS infrastructure over HashiCorp solutions. Python, go, and javascript is used as main programming languages.
	 \item [Consultoring solutions] Member of the internal consulting team to increase usage of Machine Learning on different cross areas on Mercado Libre. Helping different teams to use ML on their problems, of course using our solution.
	\end{description}}
\cventry{2009-2016}
	{Cooperative Entrepreneur}
	{Cooperativa de Trabajo Moldeo Interactive Limitada.}
	{Buenos Aires, Argentina}
	{}
	{\begin{description}
	\item [Professional Activity] Senior Consultant Analyst
	\item [Proyectos]
	\begin{description}
		\item [Moldeo] Main Developer. Open Source system to process signal and render to visualize information in real time using GPU.
		\item [Fiscal Printer on The Cloud] Main Developer. Let to Fiscal Printer connect to SAAS services in the Cloud as Chrome Application.
		\item [Argentine Odoo Localization] Main Developer. Open Source Administrative Software.
		\item [Argentine PyMES Observatory and Bolognia University] Consultant to develop Pool and Survey Automatization. Project Leader in geo-statistics information publisher for Latin America industry.
		\item [MiERP] SAAS Administrative Software.
		\item [SAS ABT Builder] Developer of ABT Builder System for SAS education Argentina.
		\item [Senior SAS Consultant] Consulter in Marketing Automation y Banking Intelligent Solutions. Technical Reference in the Software Factory of Telecom Personal.
		\item [System to search appropiated childrens during the military dictatorship] Main Designer and Developer. For the Argentine Procurator Ministry, and Sadosky Foundation.
	\end{description}
	\end{description}}
\cventry{2016-2019}
	{Associate}
	{JPMorgan Services}
	{Buenos Aires, Argentina}
	{}
	{\begin{description}
	 \item [2018-2019] Site Reliability Engineering ; Toil removing by infrastructure application automatize; CI/CD trainer.
	 \item [2016-2018] Market Data Acquisition ; EOD Jobs maintaner ; PNL reports modeling ; Process automatize; FXO/FXCash Front End Support; Move solutions to the Cloud.
         \end{description}}
\cventry{2009-2010}
	{Research in Technology for Multidisciplinary Applications.}
	{Administración Nacional de la Seguridad Social}
	{Buenos Aires, Argentina}
	{}
	{Responsible in the agreement between ANSES and the Italian Hospital of Buenos Aires to use ANSES computer capabilities to research in Genomics.}
\cventry{Feb 2008-Jul 2008}
	{Project Leader of Semantic product for Plone}
	{Inter-cultura Consultora S.A.}
	{Buenos Aires, Argentina}
	{}
	{Set of Platecom modules for Web Communities with Semantic and Multilingual support, using of Thesaurus and Ontologies structures.  http://www.platecom.com/}
\cventry{2000-2002}
	{Network and System Administrator}
	{\UBA, FCEyN, UBA.}
	{Buenos Aires, Argentina}
	{}
	{Administrator of the Network and different Process Servers. (Irix, Solaris, Tru64, Linux). Scripting in Python.}
\cventry{2000}
	{Freelance Developer}
	{}
	{}
	{}
	{Developer of a Web Accelerator in ActiveX for Internet Explorer.}
\cventry{1997-2000}
	{Informatics Assistant}
	{Colegio del Pacífico.}
	{Buenos Aires, Argentina}
	{}
	{Network Administrator. }
\cventry{1996-1997}
	{Multimedia Developer}
	{Laffont Ediciones electrónicas}
	{Buenos Aires, Argentina}
	{}
	{Main developer of ``Verbos Conjugados en Castellano''.}
\cventry{1996}
	{Junior Multimedia Developer}
	{LVD sistemas}
	{Buenos Aires, Argentina}
	{}
	{Programer in Visual BASIC 3.0 \& C++ for Windows 3.x.}
\label{profesional:hasta}


\section{Education}\label{otros:desde}

\cventry{2004-2012}
	{Delayed PHd. Student, \FCEN, \UBA.}
	{\UBA.}
	{Buenos Aires, Argentina}
	{}
	{\begin{description}
	\item [Title] Research in algorithms for protein-protein interaction prediction.
	\item [Supervisors] PhD. Adrián Turjanski, FCEN - UBA. Phd. Luis Gomez Deniz. Universidad de la Palmas de Gran Canarias.
	\end{description}}
\cventry{2002}
	{\CS}
	{\UBA.}
	{Buenos Aires, Argentina}
	{}
	{\emph{MSc Thesis:} Algorithms to identify Genomics Repetitions in Random Sequencing Methods. \emph{Supervisor:} PHd. Irene loiseau.}
\cventry{2001}
	{Trainer in Bioinformatics}
	{International Training Course on Bioinformatics (Computational Biology) Applied to Genomic. Oswaldo Cruz Foundation - UNDP/World Bank/WHO Special Programme for Research and Training in Tropical Diseases, TDR}
	{Rio de Janeiro, Brazil.}
	{}
	{http://www.who.int/tdr/publications/tdrnews/news68/bioinformatics.htm}
\cventry{1995}
	{Computer Technician.}
	{E.M.E.T. No. 8 - Otto Krause.}
	{Buenos Aires, Argentina}
	{}
	{}

\section{Skills}
\cventry{Language}
        {English}
        {Good in read, Intermediate write and talk}
        {}
        {}
        {}
\cventry{}
        {Spanish}
        {Native language}
        {}
        {}
        {}
\cventry{Project Management}
        {Agile and Traditional}
	{}
        {Scrum Participant; Waterfall V-Model ; Management techniques: Critical Path, Gantt ; Tools: Taskjuggler}
	{}
	{}
	{}
\cventry{Software Engineering}
	{Full stack designer and developer}
        {Object Oriented Design, Design by Contract ; Unit Testing, Integration Testing, Functional Testing ; DER, UML, BPML}
        {}
        {}
        {}
        {}
\cventry{Site Reliability Engineering}
        {Application, Platform and Infra structure automatization}
        {Toil identification and automatization ; DevOps process automatization ; Control Version: CVS, SVN, GitHub, Bazaar, Mercurial ; Deployment Pipelines: Jenkins as developer}
        {}
        {}
        {}
        {}
\cventry{Programming}
        {Senior}
        {Python (20 years), Javascript (7 years), R (7 years), C (10 years), C++ (12 years), CSH BASH ZSH (23 years), MathLab (5 years), SAS (3 years), Assembler (12 years)}
        {}
        {}
        {}
\cventry{}
        {Junior}
        {Java (2 years), Haskell (1 year), Ada (1 year), Eiffel (1 year), Tcl (1 year), Visual Basic (3 year)}
        {}
        {}
        {}
\cventry{Databases}
        {Modeling, Implementation and management. Query and management languages.}
        {Relational Databases: Postgresql, MySQL, Sqlite, SQLServer; NoSQL: Cassandra, MongoDB; Object Oriented: ZODB - Plone; Directories: LDAP}
        {ORM: Alchemy, Odoo}
        {}
        {}
\cventry{Cloud Computing}
        {Platform as a Service and Lambdas}
	{Cloud Foundry, AWS as Developer and SRE/DevOps}
        {}
        {}
        {}
\cventry{Machine Learning}
	{Algorithm Developer, Learning System Designer}
	{Implementation of geostatistics algorithms for common characters and proximity clustering ; ETL development for data-warehouse adaptation ; Report generation for supervised and non supervised learning algorithms ; Setup and usage of bioinformatics algorithms to query proteins functions and genes. }
        {}
        {}
        {}
        {}
\cventry{Other Technologies}
        {Integration from low level to high level abstractions.}
        {CISC, SPARK, ARM, GPU, Tesla; HTML, CSS, XSLT, YAML, CSV; IP, IPv6, ICMP, Name, SMTP, AWS, Tomcat, RPC, XML-RPC}
        {}
        {}
        {}
\cventry{Math \& Statistics Applications}
	{Researching}
	{Lineal Algebra for Computer Graphics, Molecular and Physics Simulations models. Partial differential equations for Simulation of Physics models. Correlation, Convolution (Fourier) for signal processing in 2D and 3D discrete structures for Image and Molecular processing. Solve nonlinear equations for Machine Learning and Data mining. Optimal and suboptimal solutions for discrete mathematics problems. Geostatistics for region classification. Algorithms for identify structures in pseudo-random generated strings}
	{}
	{}
	{}

\section{Teaching Background}\label{docentes:desde}

\cventry{1999-2017}
        {Teaching Assistant}
	{\DC, \FCEN, \UBA, Argentina}
	{Buenos Aires, Argentina}
	{}
	{\begin{itemize}
	\item I assisted in undergraduate and postgraduate courses for the MSc in Computer Science,
		the MSc in Geology, and the MSc in Molecular Biology for Medicine of University of Buenos Aires.
	\item Some of these course are \emph{Data Structure and Algorithms},
		\emph{Computer Organization and Architecture}, \emph{Data Bases},
		\emph{Software Engineering}, \emph{Introduction to Computer Science for Geology},
		and \emph{Introduction to Bioinformatics}.
	\end{itemize}}

\section{Scientific Background}\label{cientificos:desde}

\cventry{2009-2011}
	{Research and Develop of new Technology Laboratory}
	{Gerencia de Sistemas e Inovación Técnica, Administración Nacional de la Seguridad Social}
	{Buenos Aires, Argentina}
	{}
	{Supervisor: Phd. Mastriani, Mario.}
\cventry{2006-2009}
	{Structural Bioinformatics Laboratory, UBACYT 2008-2010}
	{\FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{Supervisor: Phd. Turjanski, Adrián.}
\cventry{2\Cuat 2007}
        {Visitor of The Roitberg Group, Computational Nano- and Bio- Physical Chemistry}
	{Quantum Theory Project, University of Florida}
	{Gainesville, FL, USA}
	{}
	{Supervisor: Phd. Roitberg Adrián.}
\cventry{2004-2012}
	{High Performance Computational Center Project, PME~2003~00084}
	{\FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{Supervisor: Phd. Marshall, Guillermo.}
\cventry{2003-2006}
        {Optimization and Extension of the Applied Genomic Center (CeGA), PME~2003~00137}
	{\FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{Supervisor: Phd. Levin, Mariano Jorge.}
\cventry{2003-2004}
	{Functional interaction between antibodies to ribosomal P proteins of Trypanosoma cruzi and cardiac receptors in chronic Chagas heart disease. HHMI 55003682 (Howard Hughes Medical Institute)}
	{\FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{Supervisor: Phd. Levin, Mariano Jorge.}
\cventry{2002-\actual}
	{Iberoamerican Bioinformatics Network (RIB)}
	{Red Iberoamericana de Bioinformática}
	{Buenos Aires, Argentina}
	{}
	{}

	\bibliographyunit
	\begin{bibunit}[plain]
		\nocite{*}
		\putbib[csrocha]
	\end{bibunit}

\section{MSc Thesis director}

\cventry{Mayo del 2008}
	{Identificacion de detalles estructurales en proteínas mediante el método de búsqueda de subgrafos isomorfos frecuentes - Identification of structure protein details by isomorph sub-graphs ; Lic. Areum Lee}
	{\DC, \FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{\emph{Supervisor:} Phd. Turjanski, Adrián; \emph{Codirector:} Lic. Cristian S. Rocha.}
\cventry{Noviembre del 2009}
	{Alineamiento de Movimientos Vibracionales para el Estudio Evolutivo de las Dinámicas de Proteínas - Vibrational movements alignments for study of evolution protein dynamics. Lic. Lucila Sanjurjo} 
	{\DC, \FCEN, \UBA.}
	{Buenos Aires, Argentina}
	{}
	{\emph{Supervisor:} Phd. Sebastian Fernandez Alberti; \emph{Codirector:} Lic. Cristian S. Rocha.}

\label{cientificos:hasta}


\end{document}
